%\special{!userdict begin /bop-hook{gsave 200 30 translate
%       65 rotate /Times-Roman findfont 216 scalefont setfont
%       0 0 moveto 0.85 setgray (DRAFT) show grestore}def end}%%%

%stylefile for "Progress in Particle and Nuclear Physics" from 20. March 2003
\documentclass[twoside,12pt]{article}
\usepackage{lineno}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{afterpage}
\usepackage{cite}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{multirow}
\usepackage{url}
\usepackage{color}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{subfig,cite}
\usepackage{colortbl}
\usepackage[]{xcolor}
\usepackage{siunitx} % For correctly displayed SI units.
\sisetup{range-phrase = \text{--}} % For correctly displayed number ranges
\usepackage{url}
\usepackage[colorlinks, citecolor=blue,anchorcolor=blue,menucolor=blue, 
linkcolor=blue,filecolor=blue,runcolor=blue,urlcolor=blue,frenchlinks=blue]{hyperref}


\def\Journal#1#2#3#4{{#1} {#2} (#4) #3 }
\def\NCA{{\em Nuovo Cimento} A}
\def\PHYS{{\em Physica}}
\def\NPA{{\em Nucl. Phys.} A}
\def\MATH{{\em J. Math. Phys.}}
\def\PRO{{\em Prog. Theor. Phys.}}
\def\NPB{{\em Nucl. Phys.} B}
\def\PLA{{\em Phys. Lett.} A}
\def\PLB{{\em Phys. Lett.} B}
\def\PLD{{\em Phys. Lett.} D}
\def\PL{{\em Phys. Lett.}}
\def\PRL{\em Phys. Rev. Lett.}
\def\PREV{\em Phys. Rev.}
\def\PREP{\em Phys. Rep.}
\def\PRA{{\em Phys. Rev.} A}
\def\PRD{{\em Phys. Rev.} D}
\def\PRC{{\em Phys. Rev.} C}
\def\PRB{{\em Phys. Rev.} B}
\def\ZPC{{\em Z. Phys.} C}
\def\ZPA{{\em Z. Phys.} A}
\def\ANNP{\em Ann. Phys. (N.Y.)}
\def\RMP{{\em Rev. Mod. Phys.}}
\def\CHEM{{\em J. Chem. Phys.}}
\def\INT{{\em Int. J. Mod. Phys.} E}
\def\r{\vec r}
\def\R{\vec R}
\def\p{\vec p}
\def\P{\vec P}
\def\q{\vec q}
\def\ss{\mbox{\boldmath $\sigma$}}
\newcommand{\nn}{\nonumber}
\topmargin-2.8cm
\oddsidemargin-1cm
\evensidemargin-1cm
\textwidth18.5cm
\textheight25.0cm

\bibliographystyle{JHEP}

\def\smallfrac#1#2{\hbox{$\frac{#1}{#2}$}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
\newcommand{\la}{\left\langle}
\newcommand{\ra}{\right\rangle}
\newcommand{\lc}{\left[}
\newcommand{\rc}{\right]}
\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}
\newcommand{\as}{\alpha_s}
\newcommand{\aq}{\alpha_s\left( Q^2 \right)}
\newcommand{\amz}{\alpha_s\left( M_Z^2 \right)}
\newcommand{\aqq}{\alpha_s \left( Q^2_0 \right)}
\newcommand{\aqz}{\alpha_s \left( Q^2_0 \right)}
\def\toinf#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow\infty }}}}
\def\tozero#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow0 }}}}
\def\toone#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow1 }}}}
\def\frac#1#2{{{#1}\over {#2}}}
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$>$}}}         %greater than or approx. symbol
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$<$}}}         %less than or approx. symbol
\newcommand{\mrexp}{\mathrm{exp}}
\newcommand{\dat}{\mathrm{dat}}
\newcommand{\one}{\mathrm{(1)}}
\newcommand{\two}{\mathrm{(2)}}
\newcommand{\art}{\mathrm{art}} 
\newcommand{\rep}{\mathrm{rep}}
\newcommand{\net}{\mathrm{net}}
\newcommand{\stopp}{\mathrm{stop}}
\newcommand{\sys}{\mathrm{sys}}
\newcommand{\stat}{\mathrm{stat}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\pdf}{\mathrm{pdf}}
\newcommand{\tot}{\mathrm{tot}}
\newcommand{\minn}{\mathrm{min}}
\newcommand{\mut}{\mathrm{mut}}
\newcommand{\partt}{\mathrm{part}}
\newcommand{\dof}{\mathrm{dof}}
\newcommand{\NS}{\mathrm{NS}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\gen}{\mathrm{gen}}
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\parr}{\mathrm{par}}
\newcommand{\val}{\mathrm{val}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\checkk}{\mathrm{check}}
\newcommand{\reff}{\mathrm{ref}}
\newcommand{\Mll}{M_{ll}}
\newcommand{\extra}{\mathrm{extra}}
\newcommand{\draft}[1]{}
%\newcommand{\comment}[1]{{\bf \it  #1}}
\def\beq{\begin{equation}}  
\def\eeq{\end{equation}}  

% Added by MU for the fast evolution section
\def\bgamma{\boldsymbol{\gamma}}
\def\nn{\nonumber}
\def \so{\sigma_I^{DIS}(x_I,Q^2_I)}
\def \sh{\frac{d\sigma^{hh}}{dX}}
\def\sdy{\frac{d\sigma^{\mathrm{DY}}}{dQ_I^2dY_I}}
\def \npdf{N_{\mathrm{pdf}}}
\def \gtilda{\tilde\Gamma_J^{\mathrm{OBS}}}
\def \n0{N_j^{(0)}}
\def \a{\alpha}
\def \b{\beta}
\def \g{\gamma}
\def \c{\xi}
\def \z{\zeta}
% Added by JR
\def\lapprox{\lower .7ex\hbox{$\;\stackrel{\textstyle <}{\sim}\;$}}
\def\gapprox{\lower .7ex\hbox{$\;\stackrel{\textstyle >}{\sim}\;$}}
\def\half{\smallfrac{1}{2}}
\def\GeV{{\rm GeV}}
\def\TeV{{\rm TeV}}
\def\ap{{a'}}
\def\vp{{v'}}
\def\e{\epsilon}
\def\d{{\rm d}}
\def\calN{{\cal N}}
\def\shat{\hat{s}}
\def\barq{\bar{q}}
\def\qq{q \bar q}
\def\uu{u \bar u}
\def\dd{d \bar d}
\def\pp{p \bar p}
\def\xa{x_{1}}
\def\xb{x_{2}}
\def\xaa{x_{1}^{0}}
\def\xbb{x_{2}^{0}}
\def\smx{\stackrel{x\to 0}{\longrightarrow}}
\def\Li{{\rm Li}}
% Added by CJM [benchmarking] % Please do not change spacing and sizing without good reason.
\def\bstar{{\color{blue}$\bigstar$}}
\def\bcirc{\raisebox{-1pt}{\scalebox{1.5}{\color{blue}$\circ$}}}
\def\rsquare{{\raisebox{-1pt}{\color{red}$\blacksquare$}}}

\newcommand{\Red}[1]{{\color{black}#1}}
\newcommand{\Blue}[1]{{\color{black}#1}}

\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
\newcommand{\tmtextit}[1]{{\itshape{#1}}}
\newcommand{\tmtextrm}[1]{{\rmfamily{#1}}}
\newcommand{\tmtexttt}[1]{{\ttfamily{#1}}}

\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\linenumbers
\vspace{.3cm}

\begin{center}
{\Large \bf Parton distributions and lattice QCD calculations:\\[0.2cm] a community white-paper}
\vspace{.4cm}

{\small 
  Huey-Wen~Lin$^{1,2}$,
  Emanuele~R.~Nocera$^6$,
  Fred~Olness$^3$,
  Kostas~Orginos$^{4,5}$,
  Juan~Rojo$^{7,8}$ (editors),
Alberto~Accardi$^{5,9}$, 
Constantia~Alexandrou$^{10,11}$, 
Alessandro~Bacchetta$^{12}$, 
Giuseppe~Bozzi$^{12}$, 
Jiunn-Wei~Chen$^{16,17}$, 	
Sara~Collins$^{13}$, 	
Mandy~Cooper-Sarkar$^{6}$, 
Martha~Constantinou$^{18}$, 
Luigi~del~Debbio$^{19}$, 
Michael~Engelhardt$^{21}$, 
Jeremy~Green$^{22}$, 
Rajan~Gupta$^{23}$, 
Lucian~Harland-Lang$^{24}$, 
Tomomi~Ishikawa$^{25}$, 
Aleksander~Kusina$^{26,27}$, 
Keh-Fei~Liu$^{28}$, 	
Simonetta~Liuti$^{29,30}$, 		
Christopher~Monahan$^{31}$, 		
Pavel~Nadolsky$^{3}$,
Jian-Wei Qiu$^{5}$,
Ingo~Schienbein$^{26}$, 	
Gerrit~Schierholz$^{32}$,
Robert Thorne$^{24}$,
Werner~Vogelsang$^{33}$,
Hartmut Wittig~$^{34}$, 
C.-P. Yuan~$^{1}$, and
James Zanotti$^{35}$
}

\vspace{.2cm}
{\it \footnotesize
~$^{1}$Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA\\
~$^{2}$Department of Computational Mathematics, Science and Engineering, \\Michigan State University, East Lansing, MI 48824, USA\\
~$^{3}$Department of Physics, Southern Methodist University, Dallas, TX 75275, USA\\
~$^{4}$Physics Department, College of William and Mary, Williamsburg, VA 23187, USA\\
~$^{5}$Thomas Jefferson National Accelerator Facility, Newport News, VA 23606, USA\\
~$^6$Rudolf Peierls Centre for Theoretical Physics, 1 Keble Road,\\ University of Oxford, OX1 3NP Oxford, United Kingdom.\\
~$^{7}$Department of Physics and Astronomy, VU University Amsterdam,\\
De Boelelaan 1081, NL-1081, HV Amsterdam, The Netherlands.\\
~$^{8}$ Nikhef, Science Park 105, NL-1098 XG Amsterdam, The Netherlands.\\
~$^{9}$ Hampton University, Hampton, VA 23668, USA.\\
~$^{10}$ Department of Physics, University of Cyprus, P.O. Box 20537, 1678 Nicosia, Cyprus. \\
~$^{11}$ Computation-based Science and Technology Research Research,\\
The Cyprus Institute, 20
Kavafi Str., Nicosia 2121, Cyprus. \\
~$^{12}$ Dipartimento di Fisica, Universit`a degli Studi di Pavia, and INFN, Sez. di Pavia, 27100 Pavia, Italy. \\
~$^{13}$ Institute for Theoretical Physics, Universit\"at Regensburg, D-93040 Regensburg, Germany. \\
~$^{14}$ Tata Institute of Fundamental Research, Homi Bhabha Road, Mumbai 400005, India. \\
~$^{16}$ Department of Physics, Center for Theoretical Sciences,
and Leung Center for Cosmology and Particle Astrophysics,
National Taiwan University, Taipei, Taiwan 106. \\
~$^{17}$ Helmholtz-Institut f\"ur Strahlen- und Kernphysik and Bethe Center
for Theoretical Physics,\\ Universit\"at Bonn, D-53115 Bonn, Germany. \\
~$^{18}$ Department of Physics, Temple University, Philadelphia, PA 19122, USA. \\
~$^{19}$ Higgs Centre for Theoretical Physics, School of
Physics and Astronomy,\\ University of Edinburgh, EH9 3FD, UK. \\
~$^{20}$ Center for Theoretical Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA. \\
~$^{21}$ Department of Physics, New Mexico State University, Las Cruces, NM 88003-8001, USA. \\
~$^{22}$ NIC, Deutsches Elektronen-Synchrotron, 15738 Zeuthen, Germany.\\
~$^{23}$ Los Alamos National Laboratory, Theoretical Division, T-2, Los Alamos, NM 87545, USA. \\
~$^{24}$ Department of Physics and Astronomy, University College London, WC1E 6BT, UK \\
~$^{25}$ T.~D.~Lee Institute, Shanghai Jiao Tong University, Shanghai, 200240, P.~R.~China. \\
~$^{26}$ Laboratoire de Physique Subatomique et de Cosmologie, Universit´e Grenoble-Alpes,\\ 
  CNRS/IN2P3, 53 avenue des Martyrs,  38026 Grenoble, France. \\
~$^{27}$ Institute of Nuclear Physics Polish Academy of Sciences, PL-31342 Krakow, Poland \\
~$^{28}$ Department of Physics and Astronomy, University of Kentucky, 
Lexington, KY 40506, USA. \\
~$^{29}$ Physics Department, University of Virginia, 382 MCormick Rd.,
Charlottesville, VA 22904, USA \\
~$^{30}$ Laboratori Nazionali di Frascati, INFN, Frascati, Italy \\
~$^{31}$ Institute for Nuclear Theory, University of Washington, Seattle, WA 98195, USA. \\
~$^{32}$ Deutsches Elektronen-Synchrotron DESY, 22603 Hamburg, Germany. \\
~$^{33}$ Institute for Theoretical Physics, T\"ubingen University, D-72076 T¨ubingen, Germany. \\
~$^{34}$ PRISMA Cluster of Excellence and Institute for Nuclear Physics 
Johannes Gutenberg University of Mainz, \\ Johann-Joachim-Becher-Weg 45, 55128 Mainz, Germany. \\
$^{35}$ CSSM, Department of Physics, The University of Adelaide, Adelaide, SA, Australia 5005.\\
}
\vspace{0.3cm}
{\it Preprint numbers:} MSUHEP-17-017, INT-PUB-17-042, IFJPAN-IV-2017-19



\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

$\quad$\\
\vspace{1.5cm}
{\bf \large Abstract}

\end{center}

The detailed understanding of the internal structure of nucleons is an active
research field with important phenomenological implications for
high-energy, nuclear, and astroparticle physics.
%
There exist two main approaches to determine the
parton distribution functions (PDFs) of the proton, which
quantify how momentum and spin 
are divided among its quark and gluon constituents.
%
The​ ​first​ ​is​ the ​global​ ​QCD​ ​analysis framework,​ ​which​ ​is​ ​based​ ​on
the​ ​factorisation​ ​of​ ​hard-scattering​ ​cross-sections​ ​into​ ​short-distance​ ​matrix​ ​elements
computable​ ​in​ ​perturbation​ ​theory​ ​and​ ​long-distance​ ​dynamics​ ​encoded​ ​in​ ​PDFs and ​exploits
constraints​ ​from​ ​experimental​ ​data​ ​to​ ​extract​ ​PDFs.
%
The second is based on the direct non-perturbative
 evaluation of PDFs
and their moments from their first-principles operator
definitions using lattice-QCD.
%
Motivated by recent progress in these two approaches
to determining proton structure, in this white-paper we present a systematic
overview of lattice-QCD calculations of PDF-related quantities, and of
their state-of-the-art evaluation from global analysis.
%
Following a review of the latest
developments in global QCD fits and lattice-QCD calculations,
we present benchmark quantities that can be
used to validate present and future
lattice-QCD calculations of proton structure.
%
We then quantify how lattice-QCD calculations could be used
to improve on present knowledge
of the unpolarised and polarised PDFs from global fits.
%
Our ultimate aim is
to establish a common language between the two communities to 
maximise and foster mutual interactions and dialogue, and to improve
understanding of the internal structure of the proton.

\clearpage

  \tableofcontents

\clearpage

\input{sec-introduction}

\input{sec-theory}

\input{sec-benchmarking}

\input{sec-projections}

\input{sec-outlook}

\appendix

\input{sec-appendix1}

\input{sec-appendix2}

\input{sec-appendix3}

% The bibliography
\bibliography{PDFLattice2017}


\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
