%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Acknowledgments}

We are very grateful to Jacqueline Gills for the flawless organization
of the workshop at Balliol College and to Michelle Bosher for
invaluable help and support with the workshop logistics.
%
This workshop was partly supported by the European Research Council via
the Starting Grant {\it ``PDF4BSM - Parton Distributions in the
  Higgs Boson Era}.
%
We also thank the DoE's Institute of Nuclear Theory at the University of Washington
in Seattle for partial support during the completion of this work. 
%
The work of HL is supposed by US National Science Foundation
under grant PHY 1653405.
%
This work is supported by
the U.S. Department of Energy under Grant No. DE-SC0010129.
%
E.~R.~N. acknowledges financial support from the
UK STFC via the Rutherford Grant ST/M003787/1.
%
J.~R. is funded by the ERC via the Starting Grant ``PDF4BSM'' and by the
Dutch Organization for Scientific Research (NWO).
%
The work of H.~L. is supposed by US National Science Foundation under grant PHY 1653405. 
%
A.~B. and G.~B. are funded by the ERC via the Consolidator
Grant “3DSPIN” (n. 647981). 
%
L.~H.~L. and R.~S.~T. would like to thank the Science and Technology Facilities Council
(STFC) for support via grant awards ST/L000377/1 and ST/P000274/1. 
%
C.~J.~M has been supported in part by the U.S.~Department of Energy through
Grant Number DE-FG02-00ER41132.
%
J.~W.~C. is partly supported by the Ministry of Science and Technology, Taiwan,
under Grant No. 105-2112-M-002-017-MY3 and the Kenda Foundation.
%
M.~C. acknowledges financial support by the U.S. Department of Energy, Office of Science, Office of Nuclear Physics, within the framework of the TMD Topical Collaboration, as well as,
by the National Science Foundation under Grant No. PHY- 1714407. 
%
K.~O. 
acknowledges financial support  by Jefferson Science Associates, LLC under U.S. DOE Contract DE-AC05-06OR23177, by U.S. DOE grant DE-FG02-04ER41302, and  by STFC consolidated grant ST/P000681/1.
